Supplementary Material \\\large{The effects of drought on land cover change and vegetation productivity in continental Chile}

### 2024-06-25 article/article_first_version/supplementary.qmd
actualizar repositorio0+

@@

The average performance metrics of ERA5L over the 266 weather stations is shown in @table_metrics_era5

@@

In the case of the 97 soil moisture stations, we averaged for the three depths (30, 60, and 90cm) and then compared it with the volumetric water content in the top 100cm of the soil derived from ERA5L. For this case, we made a daily comparison to determine the performance metrics per station, then we averaged the measured soil moisture at the three levels and over all stations.

```{r table_metrics_era5}
#| echo: false
#| tbl-cap: "Metrics of performance for the climatic and soil moisture variables from ERA5-Land with data from 266 stations in Central Chile."
tribble(~Variable,~ubRMSE,~MAE,~Bias,~CC,
        "Temperature","1.06°C","1.131°C","","0.96",
        "Precipitation","","28.1mm","1.93","0.845",
        "Soil Moisture (1m)","0.174 cc/cc","0.167 cc/cc","1.74", "0.71") |> 
  gt()
```

@@

```{=latex}
\begin{table}[!ht]
\caption{Landcover clases from IGBP MODIS and the corresponding macroclasses.}
\label{tab-landIGBPmacro}
\centering
\includegraphics[width = .3\textwidth]{../output/figs/tabla_landcover_macroclass.png}
\end{table}
```

@@

```{r fig-RF_importance}
#| echo: false
#| layout-ncol: 3
#| fig-pos: "!ht"
#| fig-env: "figure*"
#| out-width: 50%
#| fig-cap: "Error bar for the variables importance obtained from the 10 resamples folded by the Random Forest used to model land cover trend using as predictors the trend in drought indices of water supply, water demand, soil moisture, and vegetation productivity."
#| fig-subcap: 
#| - "Forest"
#| - "Cropland"
#| - "Grassland" 
#| - "Savanna"
#| - "Shrubland"
#| - "Barren Land"

@@

```{r fig-hetmaptrendzcNDVI}
#| echo: false
#| out-width: 50%
#| fig-pos: '!ht'
#| fig-cap: "Heatmap of trends in zcNDVI for 2000 to 2023 per macrozone and landcover macroclass."
knitr::include_graphics('../output/figs/heatmap_trends_zcNDVI_macro_landcover.png')
```

@@

```{r fig-r2_npp_zcNDVI}
#| echo: false
#| out-width: 50%
#| fig-pos: '!ht'
#| fig-cap: "Spatial variation of the r-squared values obtained from the yearly correlation of zcNDVI of 1, 3, 6, and 12 months with the net primary productivity (NPP) for continental Chile."
knitr::include_graphics('../output/figs/map_r2_NPP_vs_zcNDVI.png')
```

@@

>>>>

# Data

```{=latex}
\begin{table}[!ht]
\caption{Description of the satellite and reanalysis data used}
\label{tab-desEOD}
\scriptsize
\centering
\begin{tabular}{p{0.1\textwidth}cp{0.3\textwidth}p{0.095\textwidth}ccc}
\hline
\multirow{1}{*}{\centering Product} & Sub-product & Variable & Spatial Resolution  & Period & Units & Short Name \\ 
\hline
\multirow{4}{*}{ERA5L} & ~ & Precipitation & \multirow{4}{*}{~0.1°} & \multirow{4}{*}{1981-2023} & mm & P \\ 
         &  & Maximum temperature & ~ & & $°C$ & $T_{max}$ \\ 
         &  & Minimum temperature & ~ & & $°C$ & $T_{min}$ \\ 
         &  & Volumetric Soil Water Content at 1m & ~ & & $m3/m3$ & SM \\ 
ERA5L* & & Atmospheric Evaporative Demand & 0.1° & 1981-2023 & mm & AED \\
        \multirow{2}{*}{MODIS} & MOD13A3.061 & Normalized Difference Vegetation Index & \multirow{2}{*}{~1 km} & 2000-2023 & ~ & NDVI \\ 
         & MCD12Q1.061 & land cover IGBP scheme & & 2001-2022 & ~ & land cover \\ 
\hline
\end{tabular}
{\raggedright *Calculated from maximum and minimum temperatures derived from ERA5L with Eq. \ref{eq-AED}. \par}
\end{table}
```

@@

The average performance metrics of ERA5L over the weather and soil moisture stations are shown in @tbl-metricsera5. In the case of the 97 soil moisture stations, we averaged for the three depths (30, 60, and 90cm) and then compared it with the volumetric water content in the top 100cm of the soil derived from ERA5L. For this case, we made a daily comparison to determine the performance metrics per station, then we averaged the measured soil moisture at the three levels and over all stations.

@@

```{r}
#| echo: false
#| label: tbl-metricsera5
#| tbl-cap: "Metrics of performance for the climatic and soil moisture variables from ERA5-Land with data from 277 stations in Central Chile for temperature and precipitation and 99 stations of soil moisture."
tribble(~Variable,~ubRMSE,~MAE,~Bias,~CC,
        "Temperature","1.06 °C","1.13 °C","1.02","0.96",
        "Precipitation","35.5 mm","28.1 mm","1.93","0.85",
        "Soil Moisture (1m)","0.174 cc/cc","0.167 cc/cc","1.74", "0.71") |> 
  gt()
```

@@

```{=latex}
\begin{table}[!ht]
\caption{Landcover clases from IGBP MODIS and the corresponding macroclasses.}
\label{tab-landIGBPmacro}
\centering
\includegraphics[width = .5\textwidth]{../output/figs/tabla_landcover_macroclass.png}
\end{table}
```

@@

```{r fig-RF_importance}
#| echo: false
#| layout-nrow: 2
#| fig-pos: "!ht"
#| fig-env: "figure*"
#| out-width: 100%
#| fig-cap: "Error bar for the variables importance obtained from the 10 resamples folded by the Random Forest used to model land cover trend using as predictors the trend in drought indices of water supply, water demand, soil moisture, and vegetation productivity."
#| fig-subcap: 
#| - "Forest"
#| - "Cropland"
#| - "Grassland" 
#| - "Savanna"
#| - "Shrubland"
#| - "Barren Land"

@@

```{r fig-hetmaptrendzcNDVI}
#| echo: false
#| out-width: 75%
#| fig-pos: '!ht'
#| fig-cap: "Heatmap of trends in zcNDVI for 2000 to 2023 per macrozone and landcover macroclass."
knitr::include_graphics('../output/figs/heatmap_trends_zcNDVI_macro_landcover.png')
```

@@

```{r fig-r2_npp_zcNDVI}
#| echo: false
#| out-width: 75%
#| fig-pos: '!ht'
#| fig-cap: "Spatial variation of the r-squared values obtained from the yearly correlation of zcNDVI of 1, 3, 6, and 12 months with the net primary productivity (NPP) for continental Chile."
knitr::include_graphics('../output/figs/map_r2_NPP_vs_zcNDVI.png')
```

@@

# Relationship of drought indices and vegetation productivity

```{r}
#| echo: false
#| out-width: 100%
#| fig-pos: '!ht'
#| fig-cap: "Summary per land cover and study region regarding the correlation between zcNDVI with the drought indices EDDI, SPI, SPEI, and SSI for time scales of 1, 3, 6, 12, 24, and 36. The numbers in each cell indicate the time scale that reached the maximum correlation for the land cover and macrozone, and the color indicates the strength of the r-squared obtained with the index and the time scale. Cells without values indicate that the land cover type was not significant in that macrozone."
knitr::include_graphics('../output/figs/tabla_r_cor_macro_indice.png')
```

### 2024-06-25 article/article_first_version/supplementary.tex
actualizar repositorio0+

\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{colortbl}
\usepackage{array}
\usepackage{lineno}\linenumbers \usepackage{multirow} \usepackage{lscape} \newcommand{\blandscape}{\begin{landscape}} \newcommand{\elandscape}{\end{landscape}}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supplementary Material},
  pdfauthor={Francisco Zambrano; Anton Vrieling; Francisco Meza; Iongel Duran-Llacer; Francisco Fernández; Alejandro Venegas-González; Nicolas Raab; Dylan Craven},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\end{frontmatter}
    \renewcommand\thesection{S\arabic{section}}
\renewcommand\thefigure{S\arabic{figure}}
\renewcommand\thetable{S\arabic{table}}

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, enhanced, interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable]}{\end{tcolorbox}}\fi

\hypertarget{validation-of-era5l-variables}{%
\section{Validation of ERA5L
variables}\label{validation-of-era5l-variables}}

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

The average performance metrics of ERA5L over the 266 weather stations
is shown in \citet{table_metrics_era5}

In the case of the 97 soil moisture stations, we averaged for the three
depths (30, 60, and 90cm) and then compared it with the volumetric water
content in the top 100cm of the soil derived from ERA5L. For this case,
we made a daily comparison to determine the performance metrics per
station, then we averaged the measured soil moisture at the three levels
and over all stations.

\begin{longtable}{lllrr}
\caption{Metrics of performance for the climatic and soil moisture variables from
ERA5-Land with data from 266 stations in Central Chile.}\tabularnewline

\toprule
Variable & ubRMSE & MAE & Bias & CC \\ 
\midrule\addlinespace[2.5pt]
Temperature & 1.06°C & 1.131°C &  & 0.96 \\ 
Precipitation &  & 28.1mm & 1.93 & 0.845 \\ 
Soil Moisture (1m) & 0.174 cc/cc & 0.167 cc/cc & 1.74 & 0.71 \\ 
\bottomrule
\end{longtable}

\hypertarget{land-cover-macroclasses-and-validation}{%
\section{Land cover macroclasses and
validation}\label{land-cover-macroclasses-and-validation}}

\hypertarget{methods-1}{%
\subsection{Methods}\label{methods-1}}

@@

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

@@

\begin{table}[!ht]
\caption{Landcover clases from IGBP MODIS and the corresponding macroclasses.}
\label{tab-landIGBPmacro}
\centering
\includegraphics[width = .3\textwidth]{../output/figs/tabla_landcover_macroclass.png}
\end{table}

\hypertarget{relationship-between-drought-indices-and-land-cover-change}{%
\section{Relationship between drought indices and land cover
change}\label{relationship-between-drought-indices-and-land-cover-change}}

@@

\begin{figure}

\begin{minipage}[t]{0.33\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{../output/figs/fig_errorbar_resample_random_forest_trends_Forest.png}

@@

@@

\subcaption{\label{fig-RF_importance-1}Forest}
\end{minipage}%
%
\begin{minipage}[t]{0.33\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{../output/figs/fig_errorbar_resample_random_forest_trends_Cropland.png}

@@

@@

\subcaption{\label{fig-RF_importance-2}Cropland}
\end{minipage}%
%
\begin{minipage}[t]{0.33\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{../output/figs/fig_errorbar_resample_random_forest_trends_Grassland.png}

@@

@@

\subcaption{\label{fig-RF_importance-3}Grassland}
\end{minipage}%
\newline
\begin{minipage}[t]{0.33\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{../output/figs/fig_errorbar_resample_random_forest_trends_Savanna.png}

\subcaption{\label{fig-RF_importance-4}Savanna}
\end{minipage}%
%
\begin{minipage}[t]{0.33\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{../output/figs/fig_errorbar_resample_random_forest_trends_Shrubland.png}

\subcaption{\label{fig-RF_importance-5}Shrubland}
\end{minipage}%
%
\begin{minipage}[t]{0.33\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{../output/figs/fig_errorbar_resample_random_forest_trends_Barren_land.png}

\subcaption{\label{fig-RF_importance-6}Barren Land}
\end{minipage}%

@@

\end{figure}

\hypertarget{trend-of-vegetation-productivity}{%
\section{Trend of vegetation
productivity}\label{trend-of-vegetation-productivity}}

@@

{\centering \includegraphics[width=0.5\textwidth,height=\textheight]{../output/figs/heatmap_trends_zcNDVI_macro_landcover.png}

@@

\end{figure}

\hypertarget{vegetation-productivity}{%
\section{Vegetation productivity}\label{vegetation-productivity}}

@@

{\centering \includegraphics[width=0.5\textwidth,height=\textheight]{../output/figs/map_r2_NPP_vs_zcNDVI.png}

@@

\end{figure}

@@

{\centering \includegraphics[width=0.5\textwidth,height=\textheight]{../output/figs/heatmap_r2_npp_vs_zcndvi_per_landcover.png}

@@

\end{figure}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

>>>>

\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{colortbl}
\usepackage{array}
\usepackage{lineno}\linenumbers \usepackage{multirow} \usepackage{lscape} \newcommand{\blandscape}{\begin{landscape}} \newcommand{\elandscape}{\end{landscape}}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supplementary Material},
  pdfauthor={Francisco Zambrano; Anton Vrieling; Francisco Meza; Iongel Duran-Llacer; Francisco Fernández; Alejandro Venegas-González; Nicolas Raab; Dylan Craven},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\end{frontmatter}

\renewcommand\thesection{S\arabic{section}}
\renewcommand\thefigure{S\arabic{figure}}
\renewcommand\thetable{S\arabic{table}}

\section{Data}\label{data}

\begin{table}

\centering{

[!ht]

\scriptsize
\centering
\begin{tabular}{p{0.1\textwidth}cp{0.3\textwidth}p{0.095\textwidth}ccc}
\hline
\multirow{1}{*}{\centering Product} & Sub-product & Variable & Spatial Resolution  & Period & Units & Short Name \\ 
\hline
\multirow{4}{*}{ERA5L} & ~ & Precipitation & \multirow{4}{*}{~0.1°} & \multirow{4}{*}{1981-2023} & mm & P \\ 
         &  & Maximum temperature & ~ & & $°C$ & $T_{max}$ \\ 
         &  & Minimum temperature & ~ & & $°C$ & $T_{min}$ \\ 
         &  & Volumetric Soil Water Content at 1m & ~ & & $m3/m3$ & SM \\ 
ERA5L* & & Atmospheric Evaporative Demand & 0.1° & 1981-2023 & mm & AED \\
        \multirow{2}{*}{MODIS} & MOD13A3.061 & Normalized Difference Vegetation Index & \multirow{2}{*}{~1 km} & 2000-2023 & ~ & NDVI \\ 
         & MCD12Q1.061 & land cover IGBP scheme & & 2001-2022 & ~ & land cover \\ 
\hline
\end{tabular}
{\raggedright *Calculated from maximum and minimum temperatures derived from ERA5L with Eq. \ref{eq-AED}. \par}

\caption{\label{tab-desEOD}Description of the satellite and reanalysis data used}

\end{table}%

\section{Validation of ERA5L
variables}\label{validation-of-era5l-variables}

\subsection{Methods}\label{methods}

@@

\subsection{Results}\label{results}

The average performance metrics of ERA5L over the weather and soil
moisture stations are shown in Table~\ref{tbl-metricsera5}. In the case
of the 97 soil moisture stations, we averaged for the three depths (30,
60, and 90cm) and then compared it with the volumetric water content in
the top 100cm of the soil derived from ERA5L. For this case, we made a
daily comparison to determine the performance metrics per station, then
we averaged the measured soil moisture at the three levels and over all
stations.

\begin{longtable}{lllrr}

\caption{\label{tbl-metricsera5}Metrics of performance for the climatic
and soil moisture variables from ERA5-Land with data from 277 stations
in Central Chile for temperature and precipitation and 99 stations of
soil moisture.}

\tabularnewline

\toprule
Variable & ubRMSE & MAE & Bias & CC \\ 
\midrule\addlinespace[2.5pt]
Temperature & 1.06 °C & 1.13 °C & 1.02 & 0.96 \\ 
Precipitation & 35.5 mm & 28.1 mm & 1.93 & 0.85 \\ 
Soil Moisture (1m) & 0.174 cc/cc & 0.167 cc/cc & 1.74 & 0.71 \\ 
\bottomrule

\end{longtable}

\section{Land cover macroclasses and
validation}\label{land-cover-macroclasses-and-validation}

\subsection{Methods}\label{methods-1}

@@

\subsection{Results}\label{results-1}

@@

\begin{table}[!ht]
\caption{Landcover clases from IGBP MODIS and the corresponding macroclasses.}
\label{tab-landIGBPmacro}
\centering
\includegraphics[width = .5\textwidth]{../output/figs/tabla_landcover_macroclass.png}
\end{table}

\section{Relationship between drought indices and land cover
change}\label{relationship-between-drought-indices-and-land-cover-change}

@@

\begin{figure*}[!ht]

\begin{minipage}{0.33\linewidth}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{../output/figs/fig_errorbar_resample_random_forest_trends_Forest.png}

@@

\subcaption{\label{fig-RF_importance-1}Forest}

\end{minipage}%
%
\begin{minipage}{0.33\linewidth}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{../output/figs/fig_errorbar_resample_random_forest_trends_Cropland.png}

@@

\subcaption{\label{fig-RF_importance-2}Cropland}

\end{minipage}%
%
\begin{minipage}{0.33\linewidth}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{../output/figs/fig_errorbar_resample_random_forest_trends_Grassland.png}

@@

\subcaption{\label{fig-RF_importance-3}Grassland}

\end{minipage}%
\newline
\begin{minipage}{0.33\linewidth}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{../output/figs/fig_errorbar_resample_random_forest_trends_Savanna.png}

@@

\subcaption{\label{fig-RF_importance-4}Savanna}

\end{minipage}%
%
\begin{minipage}{0.33\linewidth}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{../output/figs/fig_errorbar_resample_random_forest_trends_Shrubland.png}

@@

\subcaption{\label{fig-RF_importance-5}Shrubland}

\end{minipage}%
%
\begin{minipage}{0.33\linewidth}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{../output/figs/fig_errorbar_resample_random_forest_trends_Barren_land.png}

@@

\subcaption{\label{fig-RF_importance-6}Barren Land}

\end{minipage}%

@@

\end{figure*}%

\section{Trend of vegetation
productivity}\label{trend-of-vegetation-productivity}

@@

\centering{

\includegraphics[width=0.75\textwidth,height=\textheight]{../output/figs/heatmap_trends_zcNDVI_macro_landcover.png}

@@

\end{figure}%

\section{Vegetation productivity}\label{vegetation-productivity}

@@

\centering{

\includegraphics[width=0.75\textwidth,height=\textheight]{../output/figs/map_r2_NPP_vs_zcNDVI.png}

@@

\end{figure}%

@@

\centering{

\includegraphics[width=0.5\textwidth,height=\textheight]{../output/figs/heatmap_r2_npp_vs_zcndvi_per_landcover.png}

@@

\end{figure}%

\section{Relationship of drought indices and vegetation
productivity}\label{relationship-of-drought-indices-and-vegetation-productivity}

\begin{figure}[H]

{\centering \includegraphics[width=1\textwidth,height=\textheight]{../output/figs/tabla_r_cor_macro_indice.png}

\caption{Summary per land cover and study region regarding the
correlation between zcNDVI with the drought indices EDDI, SPI, SPEI, and
SSI for time scales of 1, 3, 6, 12, 24, and 36. The numbers in each cell
indicate the time scale that reached the maximum correlation for the
land cover and macrozone, and the color indicates the strength of the
r-squared obtained with the index and the time scale. Cells without
values indicate that the land cover type was not significant in that
macrozone.}

\end{figure}%

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}
